API design for machine learning software: experiences from the scikit-learn project

### 2013-06-22 paper.tex
rename fu to union in example
For some reason, fu looks obscene to me.

fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

>>>>

union = FeatureUnion([("pca", PCA()),
                      ("kpca", KernelPCA(kernel="rbf"))])

Pipeline([("feat_union", union),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
